Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-06-02 paper/AlignedIsotropicGW.tex
Close #44.

The spin directions in isolated binary black
holes\cite{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017,MandeldeMink:2016,Marchant:2016}
are usually expected to be preferentially aligned.  Despite observed
spin-orbit misalignments in both massive stellar
binaries\cite{Albrecht:2009,2014ApJ...785...83A} and BH X-ray
binaries\cite{Orosz:2001,Martin:2008b,Martin:2008,MorningstarMiller:2014},
mass accretion and tidal interactions will tend to realign the binary.
On the other hand, a supernova natal kick (if any) can change the
orbital plane and misalign the
binary\cite{2000ApJ...541..319K,2013PhRvD..87j4028G}; the supernova
can also tilt the spin angle, as in the double pulsar
J0737-3039\cite{2011ApJ...742...81F}.  Evolutionary processes, such as
wind-driven mass loss and post-collapse fallback, can couple the spin
magnitude and direction distributions, contrary to our simplified
assumptions.  A small misalignment at wide separation can also evolve
to a more significant misalignment in component spins as the binary
spirals in through \ac{GW} emission\cite{2015PhRvD..92f4016G}, but
$\chieff$ is approximately conserved through this evolution.

>>>>

The spin directions in isolated binary black
holes\cite{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017,MandeldeMink:2016,Marchant:2016}
are usually expected to be preferentially aligned.  Despite observed
spin-orbit misalignments in massive stellar
binaries\cite{Albrecht:2009,2014ApJ...785...83A}, mass transfer and
tidal interactions will tend to realign the binary.  On the other
hand, there is some evidence of spin-orbit misalignment in black hole
X-ray
binaries\cite{Orosz:2001,Martin:2008b,Martin:2008,MorningstarMiller:2014}.
This is consistent with the expectation that a supernova natal kick
(if any) can change the orbital plane and misalign the
binary\cite{2000ApJ...541..319K,2013PhRvD..87j4028G}; the supernova
can also tilt the spin angle\cite{2011ApJ...742...81F}.  Evolutionary
processes, such as wind-driven mass loss and post-collapse fallback,
can couple the spin magnitude and direction distributions, contrary to
our simplified assumptions.  A small misalignment at wide separation
can also evolve to a more significant misalignment in component spins
as the binary spirals in through \ac{GW}
emission\cite{2015PhRvD..92f4016G}, but $\chieff$ is approximately
conserved through this evolution.
